\documentclass{hw}

\author{Jonathan Sumner Evans}
\title{Solutions to $\lambda$-Calculus Examples}
\class{CSCI 400}
\date{\today}

\begin{document}

\maketitle

\section{Alpha Equivalence}

Identify if each of the following are a valid $\alpha$-conversion.

\begin{enumerate}
    \item ${\lambda}x.{\lambda}x.x \to {\lambda}y.{\lambda}y.y$

        This is a valid $\alpha$-conversion. We rename all of the instances of
        $x$ to $y$.

    \item $\underbrace{{\lambda}x}_1.\underbrace{{\lambda}x}_2.\underbrace{x}_3 \to {\lambda}y.{\lambda}x.x$

        This is a valid alpha conversion. This is because the $x$ (3) is bound
        by the second abstraction (2), \textbf{not} by the first abstraction
        (1). Thus, by renaming the first $x$ to $y$, we end up with the term on
        the right.

        \textbf{The act of rebinding a variable is called ``variable
            shadowing''. You might want to know that for the test.}

    \item ${\lambda}x.\underbrace{{\lambda}x}_2.\underbrace{x}_3 \to
        \underbrace{{\lambda}y}_1.{\lambda}x.y$

        This is \textbf{not} a valid $\alpha$-conversion. The reason for this is
        similar to the second problem. The $x$ (3) is bound to the second
        abstraction (2) on the left hand side, however it is bound to the outer
        abstraction (1) on the right hand side.

    \item ${\lambda}x.{\lambda}y.x \to {\lambda}y.{\lambda}y.y$

        This is \textbf{not} a valid $\alpha$-conversion. The reason is that
        this introduces a \textbf{naming conflict}.

\end{enumerate}

\newpage
\section{Beta Reductions}

Fully $\beta$-reduce each of the following expressions:

\begin{enumerate}
    \setcounter{enumi}{4}
    \item In this example, I am showing the full currying steps for each
        application. Each of the applications only accepts a single term.
        \begin{align*}
            &({\lambda}x.{\lambda}y.{\lambda}f.fxy)\overbrace{({\lambda}x.{\lambda}y.y)}^{x}({\lambda}x.{\lambda}y.x)({\lambda}x.{\lambda}y.y)\\
            \rightsquigarrow&({\lambda}y.{\lambda}f.f({\lambda}x.{\lambda}y.y)y)\overbrace{({\lambda}x.{\lambda}y.x)}^{y}({\lambda}x.{\lambda}y.y)\\
            \rightsquigarrow&({\lambda}f.f({\lambda}x.{\lambda}y.y)({\lambda}x.{\lambda}y.x))\overbrace{({\lambda}x.{\lambda}y.y)}^{f}\\
            \rightsquigarrow&({\lambda}x.{\lambda}y.y)\overbrace{({\lambda}x.{\lambda}y.y)}^x({\lambda}x.{\lambda}y.x)\\
            \rightsquigarrow&({\lambda}y.y)\overbrace{({\lambda}x.{\lambda}y.x)}^y\\
            \rightsquigarrow&({\lambda}x.{\lambda}y.x).
        \end{align*}

    \item In this example, I am not showing the full currying steps for each
        application.
        \begin{align*}
            &({\lambda}a.{\lambda}b.a({\lambda}b.{\lambda}f.{\lambda}x.f(bfx))b)\overbrace{({\lambda}f.{\lambda}x.fx)}^a\overbrace{({\lambda}f.{\lambda}x.f(fx))}^b\\
            \rightsquigarrow&({\lambda}f.{\lambda}x.fx)\overbrace{({\lambda}b.{\lambda}f.{\lambda}x.f(bfx))}^f\overbrace{({\lambda}f.{\lambda}x.f(fx))}^x\\
            \rightsquigarrow&({\lambda}b.{\lambda}f.{\lambda}x.f(bfx))\overbrace{({\lambda}f.{\lambda}x.f(fx))}^b\\
            \rightsquigarrow&({\lambda}f.{\lambda}x.f(({\lambda}f.{\lambda}x.f(fx))fx))\\
            \rightsquigarrow&({\lambda}f.{\lambda}x.f(({\lambda}f.{\lambda}x.f(fx))\overbrace{f}^f\overbrace{x}^x))\\
            \rightsquigarrow&({\lambda}f.{\lambda}x.f(f(fx))).
        \end{align*}
\end{enumerate}

\end{document}
