\documentclass{exam}
\usepackage[letterpaper,margin=1in]{geometry}

\title{Homework 1}
\author{}

\makeatletter
\renewcommand\@maketitle{%
\begin{center}
    \bfseries
    \centering
    \LARGE CSCI 564: \@title
\end{center}
\bigskip
\begin{center}
\makebox[0.8\textwidth]{Name:\enspace\hrulefill\hrulefill\enspace{}CWID:\enspace\hrulefill}
\end{center}
}
\makeatother
\cfoot{Page \thepage\ of \numpages}

\begin{document}
\maketitle
\thispagestyle{foot}

\textbf{For each of the following questions, please show all of your work, and
explain your answers.}

\begin{questions}
    \question[12.5]
        Compute the Clocks Per Instruction (CPI) of a machine which has an
        average CPI for ALU operations of 1.1, a CPI for branches/jumps of 3.0,
        and a hit rate of 60\% in the cache. A hit in the cache takes 1 cycle,
        and a miss takes 120 cycles. Assume 22\% of instructions are loads, 12\%
        are stores, 20\% are branches/jumps, and the rest are ALU operations.
        Show all of the steps of your computation, and when you introduce a new
        term, explain where the term comes from.

        \vspace{\stretch{1}}

    \question[12.5]
        You are a processor designer and have to make a decision between
        building two different processors:
        \begin{enumerate}
            \item a processor which executes at 1GHz and has an average CPI of
                1.2, or
            \item a processor which executes at 2GHz but has a CPI of 2.
        \end{enumerate}
        Which is better to build? Explain your reasoning and provide
        quantitative analysis.

        \vspace{\stretch{1}}

    \newpage

    \question[12.5]
        A revolutionary new technology in memory improves your memory subsystem
        so that memory latencies are reduced by a factor of 3.5. After replacing
        your old memory with the new system, you observe that your workload now
        spends half of its time waiting for memory. What percentage of the
        original execution time of your workload (with the old memory system)
        was spent waiting for memory? Explain your answer.

        \vspace{\stretch{1}}

    \question[12.5]
        You're currently using a single-core machine, but you want to figure out
        if it's worth investing in a dual-core machine. Assuming your
        application is 60\% parallelizable, by how much could you decrease the
        core frequency while achieving the same performance? Explain your
        answer.

        \vspace{\stretch{1}}

\end{questions}

\end{document}
